% =====================================================================
%  Stargazer for Beamer — demo deck
%  A clean, modern Beamer theme: serif type, blue→black gradient title
%  bars, a top section-navigation strip, a two-tone footer, and a blue
%  rounded title box.  Swap in your own content in this file; the look
%  lives entirely in theme/stargazer-beamer.tex.
% =====================================================================
\documentclass[10pt, aspectratio=169]{beamer}
\input{theme/stargazer-beamer.tex}

\title[Stargazer for Beamer]{Stargazer for Beamer}
\subtitle{A clean, modern theme — gradient title bars, section nav, two-tone footer}
\author{Your Name}
\institute{Your Affiliation}
\date{\today}

\begin{document}

% ---------- title page (no nav / footer) ----------
{\setbeamertemplate{headline}{}\setbeamertemplate{footline}{}
\begin{frame}[plain]
  \titlepage
\end{frame}}

% ---------- agenda ----------
{\setbeamertemplate{headline}{}\setbeamertemplate{footline}{}
\begin{frame}[plain]
  \vfill
  \begin{beamercolorbox}[wd=\textwidth, sep=14pt, rounded=true, center]{title box}
    {\usebeamerfont{title}Outline}
  \end{beamercolorbox}
  \vspace{1.6em}
  \begin{itemize}\setlength{\itemsep}{0.9em}
    \item[{\color{SgBlue}\large\bfseries 1.}] {\large\textbf{Introduction}}\\[0.1em]
          \sub{What the theme gives you}
    \item[{\color{SgBlue}\large\bfseries 2.}] {\large\textbf{Layouts}}\\[0.1em]
          \sub{Columns, figures, flow diagrams}
    \item[{\color{SgBlue}\large\bfseries 3.}] {\large\textbf{Results}}\\[0.1em]
          \sub{Headline metrics and tables}
  \end{itemize}
  \vfill
  {\centering\sub{Replace this with your own talk outline.}\par}
  \vfill
\end{frame}}

% =====================================================================
\section{Introduction}

\begin{frame}{What this theme gives you}
  \begin{itemize}
    \item A \acc{blue\,$\to$\,black gradient} title bar, full-bleed across each slide.
    \item A top \acc{section-navigation} strip that tracks where you are.
    \item A two-tone footer with author, short title, and slide number.
    \item Serif body type and a single coherent \acc{accent color}.
  \end{itemize}
  \vfill
  \begin{block}{One-line swap}
    The entire look is a single \texttt{\textbackslash input} at the top of
    \texttt{slides.tex}. Keep your content; change the theme file to restyle.
  \end{block}
  \vfill
  \sub{Tip: \texttt{\textbackslash acc\{...\}} highlights in the accent color, \texttt{\textbackslash sub\{...\}} for muted secondary text.}
\end{frame}

% =====================================================================
\section{Layouts}

\begin{frame}{A two-column layout}
  \begin{columns}[T,onlytextwidth]
    \column{0.52\textwidth}
      Put text on one side and a figure on the other:
      \begin{itemize}
        \item Balanced \acc{two-column} content.
        \item Bullets, math $f(x)=\langle w, x\rangle$, and \acc{accents}.
        \item Drop a real figure in place of the box.
      \end{itemize}
      \vfill
      \sub{Use \texttt{\textbackslash figframe\{path\}\{caption\}} for a captioned image.}
    \column{0.48\textwidth}
      \placeholder[0.95]{your figure here\\[2pt]\scriptsize (\texttt{\textbackslash placeholder} or \texttt{\textbackslash includegraphics})}
  \end{columns}
\end{frame}

\begin{frame}{Flow diagrams from shared styles}
  \begin{center}
  \begin{tikzpicture}[node distance=6mm and 11mm]
    \node[flowbox] (in) {Input};
    \node[flowaccent, right=of in] (enc) {Model\\\scriptsize accent box};
    \node[flowbox, right=of enc] (dec) {Head};
    \node[flowboxw, right=of dec] (out) {Output};
    \draw[flowarr] (in) -- (enc); \draw[flowarr] (enc) -- (dec); \draw[flowarr] (dec) -- (out);
    \node[flowlbl, below=2pt of enc] {pretrained};
  \end{tikzpicture}
  \end{center}
  \vfill
  \centering\sub{Styles \texttt{flowbox}, \texttt{flowboxw}, \texttt{flowaccent}, \texttt{flowarr} and \texttt{flowlbl} ship in \texttt{theme/\_shared.tex}.}
\end{frame}

% =====================================================================
\section{Results}

\begin{frame}{Headline metrics}
  \vfill
  \metricrow{96.5}{accuracy (\%)}{2.4$\times$}{faster}{0}{labels needed}
  \vfill
  \centering\sub{\texttt{\textbackslash metricrow\{\}\{\}...} renders three big accent numbers with captions.}
\end{frame}

\begin{frame}{A results table}
  \centering {\small Benchmark — lower cost is better}\\[0.5em]
  \begin{tabular}{l c c}
    \toprule
    \textbf{Method} & \textbf{Score} & \textbf{Cost} \\
    \midrule
    Baseline      & 81.2 & high \\
    Prior work    & 88.0 & medium \\
    \textbf{This theme} & \acc{\textbf{96.5}} & \acc{low} \\
    \bottomrule
  \end{tabular}
  \vfill
  \sub{\texttt{booktabs} tables look crisp; highlight a row with \texttt{\textbackslash acc\{\}}.}
\end{frame}

% =====================================================================
\section{Closing}

\begin{frame}{Takeaways}
  \begin{enumerate}
    \item A \acc{modern}, minimal Beamer look with almost no configuration.
    \item Everything reusable lives in \texttt{theme/} — restyle in one place.
    \item Build with \acc{Tectonic}: \texttt{./build.sh} $\to$ \texttt{slides.pdf}.
  \end{enumerate}
  \vfill
  \centering\sub{Fork it, change the title, and present.}
\end{frame}

% ---------- closing (no nav / footer) ----------
{\setbeamertemplate{headline}{}\setbeamertemplate{footline}{}
\begin{frame}[plain]
  \centering\vfill
  {\fontsize{36}{40}\selectfont\color{AppleInk}Thank you.}
  \vfill
\end{frame}}

\end{document}
